Moisture absorption and drying alter nonadditive litter flammability in a mixed conifer forest

### 2020-05-25 ms/Magalhaes_Schwilk_litter_flam_moisture.tex
Minor clean up edits

\running{Litter flammability}

\author{Rita Quinones de Magalhaes$^{1,2}$ and Dylan W. Schwilk$^1$}

@@

\section*{Data and code accessibility}
All data and code for this project is at
\url{https://github.com/schwilklab/trait-flam}. Checkout git tag ``JOE.R3''
which contains this manuscript and code needed to create the figures and
tables.

>>>>

\running{Litter flammability}
\author{Rita Quinones de Magalh\~{a}es$^{1,2}$ and Dylan W. Schwilk$^1$}

@@

\section*{Data and code availability}
All data and code for this project is at
\url{https://github.com/schwilklab/trait-flam}. Checkout git tag ``JoE.1.0''
which contains this manuscript and code needed to create the figures and
tables.
